I would first like to thank my thesis adviser, Dr.\ Vallar.
Thank you for your advice and support throughout the two years of my thesis, 
as well as support during my two internships.
I would also like to thank my panelists: Dr.\ Galvez, Sir Floro, and Ma'am Jazzie.
Thank you for all the advice and support throughout my thesis.
I am honored to have been nominated for an Outstanding Thesis Award,
which was a complete surprise to me!

Next, I would like to thank my family.
Thank you for your unwavering love and support, not only throughout my college life, but throughout my whole life!
I am very grateful that you always have my back, and always reassure me that you will continue to support me in whichever career I choose or end up in.
I hope we all continue to have good health and live a comfortable and loving life.

Next, I would like to thank my college batchmates:
	Eric, Eros, Hiyam, James, Julia, Kitkat, Matthew, Naveen, Ralph, Steven, Zach, and Zy.
It's a shame that because of the pandemic, I was not able to meet you all until our third year together.
Thank you for all for the time we've spent together, and thank you for cheering me on!
We've gotten through very tough physics classes, thanks to all of your help.
We've also had so much fun spending time out of class.
May you all be successful in your careers after undergrad, whether in the academe or in the industry, whether here in the Philippines or abroad!

Next, I would like to thank all of my gaming friends, and especially my regular gaming friend group: 
	AJ, Cole, Denzel, Hannah, Mari, Nicky, and Sean.
Thank you all for the games we've played together, whether video games or tabletop role-playing games.
Even when we're not playing games, just hanging out on a Discord voice call and chatting is fun.
You've all been a great source of joy throughout the pandemic and even until now.
Spending time with you all has helped me de-stress.
I hope that we continue to have the time to play and chat with each other even after college!

Next, I would like to thank the friends I've met during the Taiwan International Internship Program:
	Aaron, Alecx, Cydee, Glen, Greg, and Janica.
Thank you for the time we've spent together during the internship.
Two months goes by very quickly, and it definitely was not enough to time for us to hang out.
Thank you all as well for sharing your own perspectives on science and academia, as they were really helpful for forming my own decisions on my career.
I wish you all the best of luck in your careers!

Next, I would like to thank the people I've worked with in my two internships:
	first at the National Metrology Laboratory at DOST-ITDI, 
	and
	second at the Institute of Atomic and Molecular Sciences in Academia Sinica's Taiwan International Internship Program
	(there are too many people to list here!).
Thank you for giving me the opportunity to work with you all.
I've been exposed to what it's like in both the government and the academe. I've gained a lot of skills, both hard and soft, and I'm sure that what I've learned in those two internships will help me in future careers.

Last but not least, I would like to thank\ldots\ \textit{myself}.
I'd like to thank myself for always being hardworking, and continuing to dream.
Times have been tough.
Really tough.
A lot of things hasn't gone the way you wished it had.
Your college life went off with a bad start because of the pandemic,
and your career may not have been what you expected it to be.
But still, you're done with undergrad, you've done an internship in Taiwan, you've accomplished some passion projects, and you've made lots of memories with friends and family. That's a very big achievement!
I wish you the best of luck in all that you do,
and I wish that your passion continues to burn bright.