This appendix chapter will briefly discuss how to install, test, and run RegCM.
This chapter will also discuss how to access the User's Guide for RegCM.
Most of the instructions are already covered in the User's Guide,
	but the other parts that were not covered will be discussed here.
	
\section{Obtaining the Model and Documentation}
	According to the User's Guide, the packed archive file with the model code can be downloaded from the G-forge website: 
		\url{http://gforge.ictp.it/gf/project/regcm/frs}.
	However, I could not access the site myself.
	Instead, I had to go into the model's GitHub site:
	\begin{center}
		\url{https://github.com/ICTP/RegCM}
	\end{center}
	to download it.
	From the GitHub website, under ``Releases'', there will be a release entitled ``NH V5 code''.
	Click on that, and you will see a link to download either a \texttt{zip} package or a \texttt{tar.gz} package.
	Download the \texttt{tar.gz} package, and extract the files from those packages using
	\begin{center}
		\texttt{tar -zxvf RegCM-5.0.0.tar.gz}.
	\end{center}
	Alternatively, if your machine has \texttt{git} and you want the most updated version of RegCM, you can use \texttt{git pull} to download the source code directly from the most recent commit to the GitHub master branch.
	Do note though, that the source code from the Releases tab may be different from the most recent commits to the master branch.

\section{Accessing the User's Guide}
	Before doing this section, do a quick Google search to see if an updated version of the RegCM User's Guide is available online.

	The User's Guide does not come as a \texttt{pdf}.
	Instead, the User's Guide comes with the RegCM source code as \LaTeX\ code.
	You will need a \LaTeX\ distribution and compile the code yourself.
	I will not discuss how to install \LaTeX\ here, but this guide in StackExchange may be helpful to you:
	\begin{center}
		\url{https://stackoverflow.com/a/1017170}.
	\end{center}

	In the source code for RegCM, there is a folder called \texttt{Doc}.
	In that folder is the \LaTeX\ source code for the User's Guide, Developer Guide, and Reference Manual, and a commented version of the input file for RegCM.
	Use your \LaTeX\ distribution to compile the \texttt{UserGuide.tex} file under the \texttt{UserGuide} folder into a readable \texttt{pdf}.
	Following the User's Guide will be very helpful for setting up, testing, and running RegCM.
	